Parallel for Oregon Zip and WRF_Grid Intersection Proportion

### 2017-03-30 r_scripts/parallel_presentation.Rmd
background

## Shapefile preparation: 2013 Oregon Zip code Shapefile and WRF Grid

Some libraries for spatial data analysis and parallel computing:
```{r, eval = FALSE}
library(rgdal)     # package for shape files
library(sp)        # spatial polygon
library(rgeos)     # rgeos package contains the intersect and area commands
library(parallel)  # parallel computing libraries
```

The **shapefile of Oregon** can be subset from the whole U.S. shapefile by filtering the zip code in Oregon State.

<br/>The **whole U.S shapefile** can be found from United States Census website:
<br/>https://www.census.gov/cgi-bin/geo/shapefiles/index.php?year=2013&layergroup=ZIP+Code+Tabulation+Areas

<br/>The **Oregon zip code** can also be found from: 
<br/>https://www.unitedstateszipcodes.org/or/

The plot below shows an Oregon State shapefile and an overlay of projected WRF Grid and Oregon shapefile.
```{r overlay, echo=FALSE}
plot(or_zip_map)
plot(smoke_grid)
plot(or_zip_map, add=T)
```

>>>>

## Background

**Goal:** Estimate population-weighted PM2.5 for each ZIP code.
<br/>
**Problem:** The population data is for WRF Grid, not ZIP code.
<br/>
**Preparation:** 2013 Oregon Zip code Shapefile and WRF Grid
<br/>
**First Step:** Calculate the proportion of intersection of ZIP code and grid box
*The plot below shows an Oregon State shapefile and an overlay of projected WRF Grid and Oregon shapefile.*
```{r overlay, echo=FALSE}
plot(or_zip_map)
plot(smoke_grid)
plot(or_zip_map, add=T)
```

**Example:** *Intersection for small area (Portland 97229); and big area (97910).*

```{r, echo = FALSE, warning=FALSE}
test_zip <- c(97229)
test_zip_map <- or_zip_map[or_zip_map$ZCTA5CE10 %in% test_zip,]

test_zip <- c(97910)
test_zip_map <- or_zip_map[or_zip_map$ZCTA5CE10 %in% test_zip,]

plot(test_zip_map)
plot(smoke_grid, add = T)
